Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-09 response/response.tex

\begin{revcomment}[2.13]
    Section 3\\
    \begin{itemize}
        \item Page 10, line 49 "mainly single-commit patches" … "small percentage 
        of data points" - give us the exact numbers for each of these.  
        \item Page 11, line 38 - define "floss refactoring" and justify how these were objectively 
        and repeatably identified in your set. You say "these cases" which makes 
        it seems that you were including the set of patches that had more than one 
        commit as your (only) floss candidates.  
    \end{itemize}
\end{revcomment}

\Us Our dataset integrates $89.3\%$ of single-commit patches and 
$10.7\%$ of patches involving more than one commit. We replaced 
line 49 by the following sentence:

\begin{quote}
    Only $10.7\%$ of the data points 
of our dataset involve more than one commits, the other
$89.3\%$ of the cases are single-commit patches.
\end{quote}

We define floss-refactoring with the paragraph below. 
To mitigate the impact of 
floss-refactorings, we extracted and manually inspected a random sample with 
    $25\%$ of security patches from each dataset. From this sample, we identified 
    $23$ floss-refactorings. Most floss-refactoring patches include many changes 
    making it difficult to understand which parts involve the security patch. 
    Although we suspect that more floss-refactorings may occur, we argue that 
    they occur in a small portion of the data.We clarified 
this in the paper:

\begin{quote}
    Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. To mitigate the impact of 
    floss-refactorings, we extracted and manually inspected a random sample with 
    $25\%$ of security patches from each dataset. From this sample, we identified 
    $23$ floss-refactorings. Most floss-refactoring patches include many changes 
    making it difficult to understand which parts involve the security patch. 
    Although we suspect that more floss-refactorings may occur, we argue that 
    they occur in a small portion of the data.
\end{quote}

@@

\Us We started with all the guidelines but after analyzing the BCH results, 
we found that some of the results for the \emph{Keep Your Codebase Small} guideline 
were way above the limit set by BCH ($20$ Person-years). We suspect this threshold 
may not be well calibrated. Thus, we decided not to consider 
this guideline in our research. We did not want 
to lose more data points. Thus, we decided to not consider the guideline for all projects.

We also did not consider the \emph{Automated Tests} guideline because
this guideline does not contemplate vulnerability scanning and penetration testing
which are the two most important testing techniques in security.

We improved the paper in the following paragraph:

\begin{quote}
    Due to BCH limitations, in particular, lack of language support 
    and project size by BCH, $308$ data points were not analyzed and automatically 
    disregarded from our study. After performing the BCH analysis and 
    the maintainability calculations, we found the following 
    limitations regarding two BCH's guidelines:

### 2021-02-09 paper/emse20.tex
small fix
more fixes

Security patches can be performed through one commit (single-commit); 
several consecutive commits (multi-commits); or, commit(s) interleaved with more 
programming activities (floss-refactoring). Only $10.7\%$ of the data points 
of our dataset involve more than one commit, the other
$89.3\%$ of the cases are single-commit patches. We manually 
inspected $25.1\%$ ($244$/$969$) of the security patches---$122$ from each dataset---and, 
identified a total of $23$ floss-refactorings. Many of these 
are patches with many changes where it is hard to understand which parts 
involve the security patch. These were disregarded to minimize the impact 
of measuring other programming activities rather than solely security patches
can have in our results.

Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were not analyzed and automatically 
disregarded from our study. After performing the BCH analysis and 
performing the maintainability calculations, we found the following 
limitations regarding two BCH's guidelines:

>>>>

Security patches can be performed through one commit (single-commit); 
several consecutive commits (multi-commits); or, commit(s) interleaved with more 
programming activities (floss-refactoring). Only $10.7\%$ of the data points 
of our dataset involve more than one commit, the other
$89.3\%$ of the cases are single-commit patches. To mitigate the impact of 
floss-refactorings, we extracted and manually inspected a random sample with 
$25\%$ of security patches from each dataset. From this sample, we identified 
$23$ floss-refactorings. Most floss-refactoring patches include many changes 
making it difficult to understand which parts involve the security patch. 
Although we suspect that more floss-refactorings may occur, we argue that 
they occur in a small portion of the data.

Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were not analyzed and automatically 
disregarded from our study. After performing the BCH analysis and the maintainability calculations, we found the following 
limitations regarding two BCH's guidelines:
